\chapter{Conclusion and Future Work}
\sffamily

\section{Conclusion}
To conclude the 2025-2026 capstone year, the aerodynamic test platform and wings (ATPW) team has made significant progress in all three of the subsections it encompasses. The goal for the test stand itself was to be able to accurately measure decoupled force produced by the MFWF under self-actuation. Through iterations in inner frame design, linking methods, and the corresponding changes in electrical components, it was determined that while the platform is capable of measuring average lift forces produced by a flapping actuator, it does so with the coupling of forces between axes in the current 6-axis frame design. As a results, the ATP developed this year has been commissioned to serve as a tool for the actuation and wing teams to compare the lift production of changing variables.

For the wings design an manufacturing, a full redesign of the wing architecture was executed to meet the revised interface requirements of the electromagnetic flapping mechanism, a structured Design of Experiments spanning two planform series, three vein splay patterns, and three chord lengths was designed, and all 40 wings were manufactured, quality controlled, and dynamically screened through drill spin testing at 30--33~Hz. A repeatable fabrication process was validated. A provisional optimal wing, R-V-C5.0 (ID:~F), was identified based on mass compliance and qualitative camber performance, pending ATP validation. The dynamic testing and motion tracking framework also established. This included the development of a dual-camera imaging system and a MATLAB-based tracking pipeline capable of extracting both in-plane and out-of-plane deformation using colour-based marker tracking. While full testing of the wing set was not completed within the project timeline, the developed framework provides a practical foundation for future validation of wing designs.

The ATPW neural-network team also established a strong two-semester foundation for machine-learning-based aerodynamic prediction. In the Fall 2025 semester, the team used a large NACA airfoil dataset as a proof-of-concept problem to compare candidate model architectures and determine an appropriate baseline workflow. This work showed that a multi-layer perceptron (MLP) was better suited than the initially explored LSTM approach for the available tabular steady-airfoil dataset, and it produced high predictive accuracy for aerodynamic coefficients including $C_L$, $C_D$, $C_M$, and $C_{DP}$. In the Winter 2026 semester, the team extended this work by consolidating the MLP results, improving the interpretation of model behavior, and beginning the transition toward a more ATP-relevant dynamic modeling framework through replication of a published PR-SSM-based method and a published sequence-to-sequence method for predicting three-dimensional unsteady aerodynamic forces and moments. Together, these two semesters of work moved the neural-network effort from initial feasibility demonstration toward a modeling workflow that is better aligned with the final flapping-wing prediction problem.


\section{Future Work}
The future work for the ATPW team is to continue design iterations in terms of the test platform, wing design, and neural network development. To be more granular, the test platform should be critically analyzed in terms of its requirements. Given the stage of development each actuator was in this year, a qualitative comparison of lift production allows for basic design changes to be made, but as the actuators are further developed, a more quantitative comparison will be required. A decision should be made on whether more resources should be expended to the current design to serve its averaged lift force measurement, or to a completely new design that focuses on precise flapping force capture and complete decoupling. Based on experience of the progression of the MFWF project, the former is more likely to be the case, but the decision should be made based on the needs of the actuation and wing teams. In any case, it is recommended that a free body diagram be constructed before manufacturing any design to serve as a quick confirmation of the design's load paths, this was arguably this years most apparent pitfall.

Future work in terms of wing design and manufacturing includes defining an interface with the concerned stakeholders, expanding the DOE or testing the existing wing set, exploring more membranes and completing ATP testing. The primary outcome of dynamic testing and motion tracking is the development of a functional dynamic testing and tracking framework, with future work focused on generating repeatable and comparable datasets across multiple wing designs. Key improvements include the use of high-speed imaging, optimized marker placement, and a more consistent flapping mechanism to improve tracking accuracy and data reliability.

Although the paper replication neural networks performed well, some improvements can be made. For the PR-SSM replication paper, it is suggested that the hyperparameter optimization loop be run with fixed datasets and fixed seeds for more iterations to achieve a higher accuracy. Once the hyperparameter have been optimized for a few fixed initial conditions, randomize the data split and the seed initialization to improve the robustness of the model. For the sequence-to-sequence paper, the model training can be run with a larger batch size and larger temporal windows to improve test accuracy and help the predicted values of the model be closer to the true values. Once these modifications have been implemented, the paper replication models should be transitioned from using the experimental data used in the papers to use experimental data generated by the ATP and RRTS to make three-dimensional force predictions, which will involve modifications to how the data is read, considering the datasets of the papers and test stands are stored in different formats. Additionally, the scope of the NACA airfoil dataset may be increased to include other designations of airfoils, such as all the available airfoils on Airfoil Tools in an attempt to further increase the model accuracy and provide more wing geometries and conditions or to extrapolate from the dataset, to help with potential future proof-of-concept problems in the ATP, RRTS, or other areas of the project that relate to neural networks.
