\chapter{Current Advances} 
\sffamily
\label{chap:Literature_Review}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%      %% 

This report is an overview of the     progress that has been made by the aerodynamic test platform and wings team during the Fall 2025 semester. As stated in the summary of this report, the breakdown of this teams structure does not follow one main result, rather it encompasses three. 

\indent For the structural aerodynamic test platform, Stan and Kevin have taken this semester to properly construct and commission it. The prototype that was fabricated from the previous capstone year had an inner frame that was unsuitable for testing, but a solid outer frame. Stan focused his efforts at the start of the semester to design and manufacture a more stable inner frame for the MFWF to securely attach to. During this time, Kevin was using the hardware that was suggested by the previous year to test the electronics for the data acquisition. Unfortunately, after running preliminary loading of the new frame while recording force data, it was discovered that the tension needed to connect the inner frame to the load cells was causing issues resolving the small forces that would be produced by the MFWF. As a result, Stan started investigating how a new design could function without needed any tension on the load cells, and Kevin went through iterations of the electronics to attempt to achieve the high resolution needed to capture the incredibly small forces the flyer will produce. For Stan and Kevin's in-depth advances, see sections \ref{chap:Stan_Melchers} and \ref{chap:Kevin_Fair}, respectfully.

{\color{red}
(Remove: From Mid-term report) For the ATP neural network, Wade and Aidan have taken on the newly assigned responsibilities to learn about and apply machine learning to the Aerodynamic Test Platform (ATP) of the MFWF. For the Fall 2025 semester, the focus was on developing an understanding of the fundamental principles, methods, and applications of machine learning and applying this knowledge, utilizing NACA airfoil data to synthesize and validate two separate aerodynamic models as a preliminary exercise. For Wade and Aidan's in-depth advances, see sections \ref{chap:Wade_Schnurr} and \ref{chap:Aidan_Sheridan}, respectively.
\par}

{\color{blue}
\indent For the ATP Neural Network, Wade and Aidan have taken taken on the newly assigned responsibilities to learn about and apply machine learning to the Aerodynamic Test Platform (ATP) of the MFWF. The fall semester involved the development of the a proof-of-concept aerodynamic mode to predict aerodynamic coefficients. Wade began with an Long Shot-Term Memory (LSTM) model and transition to a Multilayer Perceptron (MLP) model. Aidan began and developed an MLP model during the fall semester. The scope of work shifted at the beginning of the winter semester to replicate a published academic paper that utilizes similar data to the anticipated unsteady aerodynamic data from the ATP and the Rotation Rates Test Stand (RRTS) to predict non-linear aerodynamic forces and moments. Wade replicated a Probabilistic Recurrent State-Space (PR-SSM) model and Aidan replicated a sequence-to-sequence model. For Wade and Aidan's in-depth advances, see sections \ref{chap:Wade_Schnurr} and \ref{chap:Aidan_Sheridan}, respectively.
\par}

\indent As for the MFWF's wings, Abdulrahman and Justin took significant steps in designing and characterizing new functional wings for the flyer. Using the final selected wing design in 22/23 as the baseline, the goal this year is to design and manufacture more wing design prototypes and expand our wing test database and the design iteration process by including dynamic testing. The results would then be used to select the final functional pair of wings. Abdulrahman, at the start of the project, focused on a comprehensive review of published literature to define the deformation and camber that maximizes the lift generation and efficiency of the flapping wing. The second part of the semester was focused on the designing and manufacturing of new wing prototypes. Justin focused on establishing the dynamic testing process, including the tracking setup and preliminary deformation measurements to support future wing comparisons. For in-depth advances by Abdul and Justin, see sections \ref{chap:Abdulrahman_Sirajudeen-Sanni} and \ref{chap:Justin_Denneny}, respectfully.

\newpage
\section{Mechanical Design of the ATP}
\label{chap:Stan_Melchers}
\textbf{Student:} Stan Melchers
\input{Stan Melchers.tex}

\clearpage
\section{ATP Data Acquisition}
\label{chap:Kevin_Fair}
\textbf{Student:} Kevin Fair
\input{Kevin Fair.tex}

\newpage
\section{Machine Learning Development}
\label{chap:Wade_Schnurr}
\textbf{Student:} Wade Schnurr
\input{Wade Schnurr.tex}

\newpage
\section{MLP Neutral Network Development}
\label{chap:Aidan_Sheridan}
\textbf{Student:} Aidan Sheridan
\input{Aidan Sheridan.tex}

\newpage
\section{Wing Design and Manufacturing}
\label{chap:Abdulrahman_Sirajudeen-Sanni}
\textbf{Student:} Abdulrahman Sirajudeen-Sanni 
\input{Abdulrahman Sirajudeen-Sanni.tex}

\newpage
\section{Dynamic Testing and Motion Tracking}
\label{chap:Justin_Denneny}
\textbf{Student:} Justin Denneny
\input{Justin Denneny.tex}
