\chapter{Project Summary}
\sffamily
\label{chap:Project Summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Aerodynamic Test Platform and Wings (ATPW) team in the 2025-2026 year consolidates three large aspects of the overall Micro Flapping Wing Flyer (MFWF) project. The first focuses on the manufacturing and operation of a test platform for which the MFWF is to use to measure the orthogonal forces it produces under self-actuation. The previous capstone year succeeded in developing a prototype of this test platform but were plagued by hardware and shipping constraints, resulting in an insufficient amount of testing and finalization of the platform. This year, the platform was to finalized and validated for practical use by the MFWF.







{\color{red}
\indent \underline{(Remove: from mid-term report)} The second goal of the ATPW team is to develop a functional learning model that is trained on specific data recorded by the test platform and MFWF such that the forces the flyer produces are able to be predicted given the on-board telemetry. The recent advances in artificial intelligence and deep learning models across the world is the driver for this goal and, if perfected, could allow the flyer to predict it's own forces in real time.
\par}

{\color{blue}\indent The second goal of the ATPW team progressed over the Fall 2025 and Winter 2026 semesters. The Fall semester included the development and validation of an initial proof-of-concept aerodynamic prediction model using machine learning and structured, static, NACA airfoil data. The work in the Winter semester shifted towards a more physically representative prediction model of unsteady three-dimensional aerodynamic forces and moments. The progress made during this year, 2025-2026, established a foundation for future training using Aerodynamic Test Platform (ATP) and Rotational Rates Test Stand (RRTS) experimental data as it becomes available.\par}







\indent The final goal of the ATPW team this year is the finalization of the MFWF's wing structure it will use to produce the required motion for flight. The previous capstone year had performed static testing on a large variety of wing structures, but failed to capture any dynamic results and provide a concrete vein structure for the wings. This year, a comprehensive understanding of how every aspect of wing structure design can affect the motion and ultimately effectiveness of the wing is to be obtained. In coordination with the flapping mechanism team, this will result in a high performance flapper able to produce sufficient lift and accurate movement.

\indent In order to achieve the goals stated, the aerodynamic test platform and wings team have prioritized the following actions for this semester.
\begin{enumerate}
    \item Finalize and validate the aerodynamic test platform for MFWF use.
    \begin{enumerate}
        \item Manufacture an inner frame to rigidly mount the MFWF to the platform.
        \item Validate the minimum resolution and accuracy of the load cells
        \item Gain a better understanding of how the load cells can provide accurate force readings while on the test platform.
    \end{enumerate}
    \item Remanufacture the existing wing design, develop new wing prototype concepts, and develop a dynamic test setup. 
    \begin{enumerate}
        \item Modify the existing design for ease of manufacturing.
        \item Conduct a review of published literature on flapping Wing designs and testing.
        \item Design and manufacture new wing prototypes.
        \item Design and commission a dynamic test stand with high speed camera imaging.
    \end{enumerate}

    {\color{blue}\item Develop machine learning model to predict aerodynamic coefficients from static data, as a proof of concept, and then from dynamic data which share more similarities to the anticipated experimental data from the ATP and RRTS. 
        \begin{enumerate}
        \item Gain understanding of neural networks
        \item Develop a proof-of-concept machine learning application using static aerodynamic data
        \item Develop a machine learning application using a dynamic dataset comparable to anticipated experimental results from the ATP and RRTS.
        \end{enumerate}}
\end{enumerate}

